%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4

\usepackage{gensymb}
\usepackage{fixltx2e}

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

%\lastupdated % Print the Last Updated text at the top right

\namesection{Raymond}{Cutler}{ % Your name
% \urlstyle{same}\url{http://markjcutler.com} \hspace{3pt} | \hspace{3pt}   % Your website, LinkedIn profile or other web address
\href{mailto:cutler8@gmail.com}{cutler8@gmail.com} \hspace{3pt} | \hspace{3pt} 414.412.7214 % Your contact information
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.62\textwidth} % The left column takes up 66% of the text width of the page


%------------------------------------------------
% Education
%------------------------------------------------
\section{Objective}

Contribute to the growth and profitability of an organization \\ by
  solving problems and mentoring young professionals

\sectionspace

\section{Experience}

\subsection{Ceramatec, Inc. | 1984\textemdash2013}

\begin{tightitemize}
  \vspace{\topsep} % Hacky fix for awkward extra vertical space
  \item
    Invented ceramic-ceramic joining technique for a wide variety of materials
  \item
    Doubled the magnetocaloric performance of silicides for use in a magnetic refrigeration device
  \item
    Developed fluorite and perovskite ceramics for use in oxygen separation membranes
  \item
    Engineered porous and dense layers to allow cosintering in multilayer microchannel devices
  \item
    Demonstrated how additives affect the sintering kinetics and fracture toughness of SiC
  \item
    Invented a presureless-sintered SiC with high fracture toughness
  \item
    Developed borides and silicides for use in a variety of energetic applications
  \item
    Developed binderless WC made by presureless sintering and HIPing
  \item
    Developed liquid phase sintering of SiC
  \item
    Demonstrated damage-resistant ceramics using layered composites
  \item
    Demonstrated presureless sintering of Al\textsubscript{2}O\textsubscript{3}-TiC ceramic cutting tools
\end{tightitemize}

\sectionspace % Some whitespace after the section

\subsection{Adjunct Professor, University of Utah | 1996\textemdash2013}

\begin{tightitemize}
  \vspace{\topsep} % Hacky fix for awkward extra vertical space
  \item Taught materials science and materials characterization to
    over 1500 undergraduate students
  \item Mentored students as their advisor for senior theses and
    maters theses on a variety of topics
\end{tightitemize}

\sectionspace

\subsection{Elkem Research Center (Norway) | 1991\textemdash1993}

\begin{tightitemize}
  \vspace{\topsep} % Hacky fix for awkward extra vertical space
  \item
    Developed and processed a wide variety of erosion-resistant ceramic materials for use in North Sea oil applications
\end{tightitemize}

\sectionspace % Some whitespace after the section

\subsection{Terra Tek, Inc. | 1979\textemdash1983}

\begin{tightitemize}
  \vspace{\topsep} % Hacky fix for awkward extra vertical space
\item
    Developed lightweight ceramic proppants for deep gas well stimulation
  \item
    Characterized fracture toughness of cemented carbides relative to binder chemistry
\end{tightitemize}

\sectionspace

\subsection{Fansteel Research Center | 1977\textemdash1979}

\begin{tightitemize}
  \vspace{\topsep} % Hacky fix for awkward extra vertical space
  \item
    Developed Al\textsubscript{2}O\textsubscript{3}-TiC poweder synthesis by exothermic reactions for ceramic cutting tools
\end{tightitemize}

\sectionspace % Some whitespace after the section

\section{Education}


\descript{Ph.D. | Materials Science and Engineering}
\location{University of Utah 1984}

\sectionspace

\descript{M.S. | Materials Science and Engineering}
\location{University of Utah 1977}

\sectionspace

\descript{B.A. | Chemistry}
\location{University of Utah 1976}


\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.33\textwidth} % The right column takes up 33% of the text width of the page


%------------------------------------------------
% Professional Interests
%------------------------------------------------

% \section{Professional Interests}

% Real-world robotics, perception, controls, learning, planning

% \sectionspace % Some whitespace after the section



\section{Honors}

\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Student’s choice teaching award (University of Utah, 2007)
\item College of Engineering teaching award (University of Utah, 2010)
\item Author of over 70 peer reviewed scientific articles
\item 17 patents
\end{tightitemize}

\sectionspace
\sectionspace
\sectionspace
\sectionspace


%------------------------------------------------
% Skills
%------------------------------------------------

\section{Skills}

\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Research and developement
\item Materials characterization
\item Teaching and mentoring
\item Leadership and vision
\item Materials processing
\item Problem solving
\item Communication
\item Innovation
\end{tightitemize}

\sectionspace
\sectionspace
\sectionspace
\sectionspace

\section{Tools}

\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item XRD
\item SEM/EDS
\item K\textsubscript{Ic}, Hv, $\color{headings} \sigma$\textsubscript{f}, $\color{headings} \kappa$
\item TGA/DTA/DSC
\end{tightitemize}

\sectionspace % Some whitespace after the section
\sectionspace
\sectionspace
\sectionspace

%------------------------------------------------
% Volunteer Experience
%------------------------------------------------
\section{Volunteer}

\subsection{The Church of Jesus Christ of
  Latter-day Saints}

\descript{Leadership and Vision}

\location{Wisconsin Milwaukee Mission, President | 2013\textemdash2016}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Directed, trained, and taught over 500 full-time volunteer
  missionaries serving for the Church of Jesus Christ of Latter-day
  Saints in Wisconsin and Michigan.
\end{tightitemize}

\sectionspace % Some whitespace after the section


%----------------------------------------------------------------------------------------


\end{minipage} % The end of the right column

%------------------------------------------------
% Selected Publications
%------------------------------------------------

\newpage

\section{Selected Publications}

\begin{tightitemize}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\item \textbf{R. A. Cutler} and A. V. Virkar, ``The Effect of Binder
  Thickness and Residual Stresses on the Fracture Toughness of
  Cemented Carbides,'' J. Mater. Sci. 20, 3557-3573 (1985).
\item \textbf{R. A. Cutler}, ``Engineering Properties of Borides,''
  Engineered Materials Handbook, Vol. 4: Ceramics and Glasses, ed. by
  C. A. Dostal, (ASM, Materials Park, OH pp. 787-803 1991).
\item T. B. Jackson, A. V. Virkar, K. L. More, R. B. Dinwiddie, and
  \textbf{R. A. Cutler}, ``High Thermal Conductivity AlN Ceramics: The
  Effect of Thermodynamic, Kinetic, and Microstructural Factors,''
  J. Am.  Ceram. Soc., 80[6], 1421-35 (1997).
\item M. Flinders, D. Ray, A. Anderson, and \textbf{R. A. Cutler},
  ``High-Toughness Silicon Carbide as Armor,'' J. Am. Ceram. Soc.,
  88[8], 2217-26 (2005).
\item K. N. Hutchings, J. Bai, \textbf{R. A. Cutler}, M. A. Wilson,
  and D. L. Taylor, ``Electrochemical Oxygen Compression Using Planar,
  Cosintered Ceramics,'' Solid State Ionics, 179, 442-450 (2008).
\item M. L. Whittaker and \textbf{R. A. Cutler}, ``Effect of Synthesis
  Atmosphere, Wetting, and Compaction on the Purity of AlB\textsubscript{2},''
  J. Solid St. Chem., 201 93-100 (2013).
\end{tightitemize}

\sectionspace
\sectionspace
\sectionspace
\sectionspace

\section{References}
\begin{minipage}[t]{0.55\textwidth} % The left column takes up 66% of the text width of the page

\descript{Dr. Anil V. Virkar}
\location{Distinguished Professor | University of Utah}
\location{Department of Materials Science}
122 South Central Campus Drive \\
Salt Lake City, Utah 84112 \\
tel. 801.581.5396 \\
email: \href{anil.virkar@m.cc.utah.edu}{anil.virkar@m.cc.utah.edu} \\

\sectionspace

\descript{Dr. Darryl P. Butt}
\location{Professor and Chair | Boise State University}
\location{Department of Materials Science}
1910 University Drive \\
Boise, Utah 83725 \\
tel: 208.426.1054 \\
email: \href{darrylbutt@boisestate.edu}{darrylbutt@boisestate.edu} \\


\end{minipage}
\hfill
\begin{minipage}[t]{0.4\textwidth} % The right column takes up 33% of the text width of the page

\descript{Dr. S. Elangovan}
\location{Research Scientist | Ceramatec, Inc.}
2425 South 900 West \\
Salt Lake City, Utah 84119 \\
tel: 801.978.2162 \\
email: \href{elango@ceramatec.com}{elango@ceramatec.com} \\

\sectionspace

\descript{Robert K. Lake}
\location{CPA}
1860 South 1150 East \\
Bountiful, Utah 84010 \\
tel: 801.298.0879 \\
email: \href{blake@eidebailly.com}{blake@eidebailly.com} \\

\sectionspace

\end{minipage} % The end of the right column

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
